Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Final State with Multivariate Techniques

### 2015-12-15 paper/sec-intro.tex
working on the text

The measurement of double Higgs production will be one of the central
physics goals of the LHC program in its recently started high-energy
phase, as well as for its future high-luminosity upgrade (HL-LHC)
which aims to accumulate a total integrated
luminosity of 3 ab$^{-1}$~\cite{ATLAS:2013hta,CMS:2013xfa}.
%
Higgs pair production is directly sensitive to the
Higgs trilinear coupling $\lambda$~\cite{baglio} and 
provides crucial
information on the electroweak symmetry breaking mechanism.
%
It also probes the underlying strength of the Higgs interactions
at high energies, and can be used to test the composite nature of the 
Higgs boson~\cite{Giudice:2007fh,Contino:2010mh}.
%
While Standard Model (SM) cross-sections are small,
many Beyond the SM (BSM)
scenarios predict enhanced rates for double Higgs production, therefore searches have already been performed by ATLAS and CMS with Run I data~\cite{Aad:2015xja,Aad:2015uka,Aad:2014yja,Khachatryan:2015yea,Chatrchyan:2011wt}
and will continue at Run II.
%
The study of Higgs pair production will also be relevant to
any future high-energy 
collider, either at a 100 TeV circular machine~\cite{Arkani-Hamed:2015vfh,Barr:2014sga,Papaefstathiou:2015iba,Azatov:2015oxa} or at
a linear or circular electron-positron collider~\cite{Contino:2013gna}.

Analogously to single Higgs production~\cite{Dittmaier:2012vm}, 
in the SM the dominant mechanism for the production of a pair of
Higgs bosons at the LHC is 
gluon fusion (see Refs.~\cite{baglio,Frederix:2014hta} and
references therein).
%
For a center-of-mass energy of $\sqrt{s} = 14\,$TeV, the
next-to-next-to-leading order (NNLO)
total cross section is approximately $40\,$fb~\cite{deFlorian:2013jea},
which is increased by a further few percent once
next-to-next-to-leading logarithmic
(NNLL) corrections
are accounted for~\cite{deFlorian:2015moa}.
%
Feasibility studies in the case of a SM-like Higgs boson
in the gluon-fusion channel
at the LHC have been performed for different final states, including
$b\bar b\gamma\gamma$~\cite{Baur:2003gp,Barger:2013jfa},
$b\bar{b}\tau^+\tau^-$~\cite{Baur:2003gpa,Barr:2013tda,Dolan:2012rv,Dolan:2013rja},
$b\bar{b}W^+W^-$~\cite{Dolan:2012rv,Papaefstathiou:2012qe} and
$b\bar{b}b\bar{b}$~\cite{Baur:2003gpa,Dolan:2012rv,Wardrope:2014kya,deLima:2014dta,Barger:2013jfa}.
%
While these studies differ in their quantitative conclusions,
a consistent picture emerges 
that the ultimate precision in the determination of the Higgs trilinear
coupling $\lambda$ requires the full integrated luminosity
of the HL-LHC, $\mathcal{L}=3$ ab$^{-1}$,
and will rely on the combination of all relevant final states.

In addition to the gluon-fusion production mode, Higgs pairs
can also be produced in the vector-boson fusion
channel $hhjj$~\cite{Contino:2010mh,Dolan:2013rja,Dolan:2015zja,
  Brooijmans:2014eja},
the associated production modes
$hhW$ and $hhZ$~\cite{Barger:1988jk,baglio,Cao:2015oxx}
(also known as Higgs-Strahlung),
and also in association
with top quark pairs $hht\bar{t}$~\cite{Englert:2014uqa}.
%
All of these channels are challenging due to the small production
rates: at 14 TeV, the inclusive total cross-sections are
2.0 fb for VBF $hhjj$~\cite{Liu-Sheng:2014gxa},
0.5 fb for $W(Z)hh$~\cite{baglio}
and 1.0 for $hht\bar{t}$~\cite{Englert:2014uqa}.
%
The interplay between  kinematic
distributions for the
extraction of $\lambda$ from the measured
cross-sections, and the role of the associated theoretical
uncertainties, have been intensely scrutinized
recently~\cite{Slawinska:2014vpa,Chen:2014xra,Goertz:2013kp,
  Frederix:2014hta,Dawson:2015oha,Maltoni:2014eza,Maierhofer:2013sha,Grigo:2013rya,Grigo:2014jma}.
%

While the SM production rates for Higgs
pairs are small, they can be substantially
enhanced in a variety of BSM scenarios.
%
Feasibility studies of Higgs pair production in New Physics
models have been performed in a number of different frameworks,
including Effective Field
Theories (EFTs) with higher-dimensional
operators and anomalous 
Higgs couplings~\cite{Nishiwaki:2013cma,Dall'Osso:2015aia,Azatov:2015oxa,Liu:2014rba,Goertz:2014qta,He:2015spf,Grober:2015cwa}, resonant production
in models such as extra dimensions~\cite{Gouzevitch:2013qca,Cooper:2013kia,No:2013wsa,Wen-Juan:2015gqg}, and Supersymmetry and
Two Higgs Doublet models (2HDMs)~\cite{Belyaev:1999kk,Han:2013sga,Hespel:2014sla,Wu:2015nba,Cao:2014kya,Ellwanger:2013ova}.
%
Since BSM dynamics modify
the kinematic distributions of the Higgs decay products, for
instance boosting the di-Higgs system,
different analysis strategies  might be required for BSM
Higgs pair searches as compared to SM measurements.

@@

In the context of SM production,
the main advantage of the $b\bar{b}b\bar{b}$ final state is the
enhancement of the signal yield
from the large branching fraction of Higgs bosons into bottom-anti-bottom
pairs, ${\rm BR}\lp H\to b\bar{b}\rp\simeq 0.57$~\cite{Dittmaier:2012vm}.
%
However a measurement in this channel
needs to deal with an overwhelming QCD multi-jet background.
%
Recent studies of Higgs pair production in this
final state~\cite{Wardrope:2014kya,deLima:2014dta}
estimate that, for an integrated
luminosity of
$\mathcal{L}=3$ ab$^{-1}$,
a signal significance of around $S/\sqrt{B}\sim 2.0$ could be obtained.
%
While irreducible backgrounds, such as $4b$ and
$t\bar{t}$, are included in these analysis, the contribution
from reducible processes, such as $bbjj$ and
$jjjj$, which can contribute to the signal yield when 
light jets are mis-identified as $b$-jets,
are not accounted for.
%
As we will show, due to both
selection effects and $b$-quark radiation in the
parton shower, the
contribution of the $2b2j$ process is as significant as
the irreducible $4b$ component.

@@

The structure of this paper proceeds as follows.
%
In Sect.~\ref{mcgeneration} we present the modeling of the signal
and background processes with Monte Carlo event generators.
%
In Sect.~\ref{sec:analysis}
we introduce our analysis strategy, in particular
the classification of individual events into
different categories according to their topology.
%
Results of the cut-based analysis
are then presented in Sect.~\ref{sec:results}.
%
In Sect.~\ref{sec:mva} we illustrate the enhancement of signal
significance using multivariate techniques, and
assess the robustness of our results against the effects of PU.
%
In Sect.~\ref{sec:conclusions} we conclude and outline
future studies to extend our results to estimate the accuracy
in the determination of trilinear coupling $\lambda$, as well as
to provide
 constraints in
BSM scenarios.

>>>>

The measurement of double Higgs production will be one of the central
physics goals of the LHC program in its recently started high-energy
phase, as well as for its future high-luminosity upgrade (HL-LHC)
which aims to accumulate a total integrated
luminosity of 3 ab$^{-1}$~\cite{ATLAS:2013hta,CMS:2013xfa}.
%
Higgs pair production~\cite{baglio} is directly sensitive to the
Higgs trilinear coupling $\lambda$ and 
provides crucial
information on the electroweak symmetry breaking mechanism.
%
It also probes the underlying strength of the Higgs interactions
at high energies, and can be used to test the composite nature of the 
Higgs boson~\cite{Giudice:2007fh,Contino:2010mh}.
%
While Standard Model (SM) cross-sections are small,
many Beyond the SM (BSM)
scenarios predict enhanced rates for double Higgs production, therefore searches have already been performed by ATLAS and CMS with Run I data~\cite{Aad:2015xja,Aad:2015uka,Aad:2014yja,Khachatryan:2015yea,Chatrchyan:2011wt}
and will continue at Run II.
%
The study of Higgs pair production will also be relevant to
any future high-energy 
collider, either at a 100 TeV circular machine~\cite{Arkani-Hamed:2015vfh,Barr:2014sga,Papaefstathiou:2015iba,Azatov:2015oxa} or at
a linear or circular electron-positron collider~\cite{Contino:2013gna}.

Analogously to single Higgs production~\cite{Dittmaier:2012vm}, 
in the SM the dominant mechanism for the production of a pair of
Higgs bosons at the LHC is 
gluon fusion (see~\cite{baglio,Frederix:2014hta} and
references therein).
%
For a center-of-mass energy of $\sqrt{s} = 14\,$TeV, the
next-to-next-to-leading order (NNLO)
total cross section is approximately $40\,$fb~\cite{deFlorian:2013jea},
which is increased by a further few percent once
next-to-next-to-leading logarithmic
(NNLL) corrections
are accounted for~\cite{deFlorian:2015moa}.
%
Feasibility studies in the case of a SM-like Higgs boson
in the gluon-fusion channel
at the LHC have been performed for different final states, including
$b\bar b\gamma\gamma$~\cite{Baur:2003gp,Barger:2013jfa},
$b\bar{b}\tau^+\tau^-$~\cite{Baur:2003gpa,Barr:2013tda,Dolan:2012rv,Dolan:2013rja},
$b\bar{b}W^+W^-$~\cite{Dolan:2012rv,Papaefstathiou:2012qe} and
$b\bar{b}b\bar{b}$~\cite{Baur:2003gpa,Dolan:2012rv,Wardrope:2014kya,deLima:2014dta,Barger:2013jfa}.
%
While these studies differ in their quantitative conclusions,
a consistent picture emerges 
that the ultimate precision in the determination of the Higgs trilinear
coupling $\lambda$ requires the full integrated luminosity
of the HL-LHC, $\mathcal{L}=3$ ab$^{-1}$,
and will rely on the combination of all relevant final states.

In addition to the gluon-fusion channel, Higgs pairs
can also be produced in the vector-boson fusion
channel $hhjj$~\cite{Contino:2010mh,Dolan:2013rja,Dolan:2015zja,
  Brooijmans:2014eja},
the associated production modes
$hhW$ and $hhZ$~\cite{Barger:1988jk,baglio,Cao:2015oxx}
(also known as Higgs-Strahlung),
and also in association
with top quark pairs $hht\bar{t}$~\cite{Englert:2014uqa}.
%
All of these channels are challenging due to the small production
rates: at 14 TeV, the inclusive total cross-sections are
2.0 fb for VBF $hhjj$~\cite{Liu-Sheng:2014gxa},
0.5 fb for $W(Z)hh$~\cite{baglio}
and 1.0 for $hht\bar{t}$~\cite{Englert:2014uqa}.
%
The interplay between  kinematic
distributions for the
extraction of $\lambda$ from the measured
cross-sections, and the role of the associated theoretical
uncertainties, have been intensely scrutinized
recently~\cite{Slawinska:2014vpa,Chen:2014xra,Goertz:2013kp,
  Frederix:2014hta,Dawson:2015oha,Maltoni:2014eza,Maierhofer:2013sha,Grigo:2013rya,Grigo:2014jma}.
%

While the SM production rates for Higgs
pairs are small, they are substantially
enhanced in a variety of BSM scenarios.
%
Feasibility studies of Higgs pair production in New Physics
models have been performed in a number of different frameworks,
including Effective Field
Theories (EFTs) with higher-dimensional
operators and anomalous 
Higgs couplings~\cite{Nishiwaki:2013cma,Dall'Osso:2015aia,Azatov:2015oxa,Liu:2014rba,Goertz:2014qta,He:2015spf,Grober:2015cwa}, resonant production
in models such as extra dimensions~\cite{Gouzevitch:2013qca,Cooper:2013kia,No:2013wsa,Wen-Juan:2015gqg}, and Supersymmetry and
Two Higgs Doublet models (2HDMs)~\cite{Belyaev:1999kk,Han:2013sga,Hespel:2014sla,Wu:2015nba,Cao:2014kya,Ellwanger:2013ova}.
%
Since BSM dynamics modify
the kinematic distributions of the Higgs decay products, for
instance boosting the di-Higgs system,
different analysis strategies  might be required for BSM
Higgs pair searches as compared to SM measurements.

@@

In the context of SM production,
the main advantage of the $b\bar{b}b\bar{b}$ final state is the
enhancement of the signal yield
from the large branching fraction of Higgs bosons into
$b\bar{b}$
pairs, ${\rm BR}\lp H\to b\bar{b}\rp\simeq 0.57$~\cite{Dittmaier:2012vm}.
%
However a measurement in this channel
needs to deal with an overwhelming QCD multi-jet background.
%
Recent studies of Higgs pair production in this
final state~\cite{Wardrope:2014kya,deLima:2014dta}
estimate that, for an integrated
luminosity of
$\mathcal{L}=3$ ab$^{-1}$,
a signal significance of around $S/\sqrt{B}\sim 2.0$ can be obtained.
%
In these analysis, irreducible backgrounds such as $4b$ and
$t\bar{t}$ are included, however the
reducible components, in particular as $bbjj$ and
$jjjj$, are neglected.
%
These can contribute to the signal yield when 
light and charm jets are mis-identified as $b$-jets.
%
Indeed, due to both
selection effects and $b$-quark radiation in the
parton shower, the
contribution of the $2b2j$ process is as significant as
the irreducible $4b$ component.

@@

The structure of this paper proceeds as follows.
%
In Sect.~\ref{mcgeneration} we present the modeling of the signal
and background processes with Monte Carlo event generators.
%
In Sect.~\ref{sec:analysis}
we introduce our analysis strategy, in particular
the classification of individual events into
different categories according to their topology.
%
Results of the cut-based analysis
are then presented in Sect.~\ref{sec:results}.
%
In Sect.~\ref{sec:mva} we illustrate the enhancement of signal
significance using multivariate techniques, and
assess the robustness of our results against the effects of PU.
%
In Sect.~\ref{sec:conclusions} we conclude and outline
future studies to estimate the accuracy
in the determination of the trilinear coupling $\lambda$ and
to provide
 constraints in
BSM scenarios.

### 2015-12-15 paper/sec-mcsamples.tex
working on the text

Higgs pair production is simulated at leading order (LO) using
{\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}.
%
We use a tailored  model~\cite{Maltoni:2014eza}
for gluon-fusion Higgs boson pair production
which includes mass effects
from the
exact form factors for the top-quark triangle and box
loops~\cite{Plehn:1996wb}.
%
Equivalent results can be obtained using
the recently available functionalities
for the calculation of loop-induced processes
in {\tt MadGraph5\_aMC@NLO}~\cite{Hirschi:2015iia}.
%
The calculation is performed in the
$n_f$=4 scheme,  accounting for  $b$-quark mass effects. 
The renormalization and factorization
scales are taken to be $\mu_F=\mu_R=H_T/2$,
with
\be
H_T\equiv \sum_i \sqrt{p_{T,i}^2+m_i^2} \, ,
\ee
the scalar sum of the
transverse masses of all final state particles.
%
For the input parton distribution functions (PDFs) we 
adopt the NNPDF 3.0 $n_f = 4$ LO set~\cite{Ball:2014uwa} with
$\alpha_s(m_Z^2)=0.118$,
interfaced via {\tt LHAPDF6}~\cite{Buckley:2014ana}.
%
The Higgs boson couplings
and branching ratios are set to their SM values,
and its mass is taken to be
$m_h=125$ GeV~\cite{Aad:2014aba,Khachatryan:2014jba,Aad:2015zhl}.
%
In the SM, the Higgs trilinear coupling
is given by $\lambda=m_h^2/2v^2$, with $m_h=125$ GeV
the Higgs boson mass and $v\simeq 246$ GeV the Higgs vacuum expectation
value (vev).
%

@@

In Fig.~\ref{fig:hhFeyn} we show representative Feynman diagrams
    for LO Higgs pair production in gluon fusion.
    %
    The non-trivial interplay between the heavy quark box and the triangle loop diagrams
    can lead to either constructive or destructive interference
    and complicates the extraction of
    the trilinear coupling
    $\lambda$ from the measurement of the Higgs pair
    production cross-section.
    %
    Higher order corrections~\cite{deFlorian:2013jea,Frederix:2014hta}
    are dominated by gluon radiation
    from either the initial state gluons or from the heavy quark loops.

    The total inclusive cross-section for this processes is
    known up to NNLO~\cite{deFlorian:2013jea}.
    %
    Resummed NNLO+NNLL calculations for Higgs pair production are
    also available~\cite{deFlorian:2015moa},
leading to a moderate enhancement of the order of
few percent as compared to the fixed-order NNLO calculation.
%
To achieve the correct higher-order value of the
integrated cross-section, we rescale our LO signal sample to match the
NNLO+NNLL
inclusive calculation.
%
This corresponds to
a $K$-factor $\sigma_{\rm NNLO+NNLL}/\sigma_{\rm LO}=2.4$, as indicated
in Table~\ref{tab:samples}.
%
Parton level signal events are then showered with the {\tt Pythia8} Monte
Carlo~\cite{Sjostrand:2007gs,Sjostrand:2014zea}, version {\tt v8.201}.
%
We use the default settings for the modeling
of the underlying event (UE), multiple parton
interactions (MPI), and pile-up (PU), by means
of the Monash 2013 tune~\cite{Skands:2014pea},
based on the NNPDF2.3LO PDF set~\cite{Ball:2012cx,Ball:2013hta}.
%

\subsection{Backgrounds: QCD multijet and $t\bar{t}$ production}

Background samples are generated at leading order
with the {\tt SHERPA} event generator~\cite{Gleisberg:2008ta}, {\tt v2.1.1}.
%
As in the case of the signal generation,
the NNPDF 3.0 $n_f = 4$ LO set with strong coupling
$\alpha_s(m_Z^2)=0.118$ is used for all samples, and
we use as
factorisation and renormalisation scales $\mu_F=\mu_R=H_T/2$.
%
We account for the most relevant background
processes that can mimic the
 $hh\to 4b$ signal process.
%
This includes  QCD $4b$ multi-jet production, as well as
QCD $2b2j$ and $4j$ production, and top quark pair
production.
%
The latter is restricted to the fully hadronic final state,
since 
leptonic decays of top quarks can be removed by requiring
a lepton veto.
%
Single Higgs production processes such as $Z(\to b\bar{b})h(\to b\bar{b})$
and $t\bar{t}h(\to b\bar{b})$ along with electroweak backgrounds e.g $Z(\to b\bar{b})b\bar{b}$,
are much smaller than the QCD backgrounds~\cite{Wardrope:2014kya,deLima:2014dta}
and are therefore not included in the present analysis.
%

The LO cross-sections for
the background samples have been rescaled so that the integrated
distributions reproduce known higher-order QCD results.
%
For the $4b$ and $2b2j$ samples NLO/LO $K$-factors of 1.6 and 1.3
respectively have been determined
using {\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}.
%
For the $4j$ sample, we rescale the LO cross-section
using the {\tt BLACKHAT}~\cite{Bern:2011ep}
calculation, resulting in
an NLO/LO $K$-factor of 0.6.
%
Finally, the LO cross-section for $t\bar{t}$ production has been rescaled
to match the NNLO+NNLL calculation of Ref.~\cite{Czakon:2013goa}, leading
to a $K$-factor of 1.4.
%
The $K$-factors that we use to rescale
the signal background samples are summarised in
Table~\ref{tab:samples}.

 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
  \small
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Process &  Generator & $N_{\mathrm{evt}}$ & $\sigma_{\mathrm{LO}}$ (pb)  & $K$-factor \\
\hline
\hline
$pp \to hh$ &  {\tt MadGraph5\_aMC@NLO} & 1M & $1.7\cdot10^{-2}$  &  2.4  (NNLO+NNLL~\cite{deFlorian:2013jea,deFlorian:2015moa}) \\
\hline
\hline
$pp \to b\bar{b}b\bar{b}$ &  {\tt SHERPA}v2.1.1 & 3M &$1.1 \cdot10^3$  & 1.6 (NLO~\cite{Alwall:2014hca}) \\
$pp \to b\bar{b}jj$ &  {\tt SHERPA}v2.1.1 & 3M & $2.7 \cdot 10^5$ & 1.3 (NLO~\cite{Alwall:2014hca}) \\
$pp \to jjjj$ &  {\tt SHERPA}v2.1.1 & 3M  & $9.7\cdot 10^6$ &  0.6 (NLO~\cite{Bern:2011ep})\\
$pp \to t\bar{t}\to b\bar{b}jjjj$ &  {\tt SHERPA}v2.1.1 & 3M & $2.5\cdot 10^3$   & 1.4 (NNLO+NNLL~\cite{Czakon:2013goa})\\
\hline
\end{tabular}
\caption{\small Details of the signal and background Monte
  Carlo samples used in this work.
  %
  For top quark production, only the hadronic final state is generated.
  %
We also provide the corresponding inclusive $K$-factor
  which is applied to reproduce the known
  higher-order results. \label{tab:samples}
} 
\end{center}
\end{table}%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

At the generation level, the following loose selection 
cuts are applied to
background events.
%
Each final state particle in the hard process must have $p_T \ge 20$ GeV, and be located
in the central  rapidity
region with
$| \eta | \le 3.0$.
%
At the matrix-element level
all final state particles must also be separated by a minimum $\Delta R_{\mathrm{min}} =0.1$.
%
We have checked that these generator-level cuts are loose enough to have
no influence over the analysis cuts.
%
From Table~\ref{tab:samples}
we see that the $t\bar{t}$ and QCD $4b$ cross-sections are of
the same order of magnitude. However the former can be efficiently
reduced by using top quark reconstruction criteria.
%
The $bbjj$ cross-section is more than two orders
of magnitude larger than the $4b$ result, but will be suppressed
by the light and charm jet mis-identification rates,
required to contribute to the $4b$ final state.

@@

To account for the finite angular resolution of the calorimeter,
the $\eta$-$\phi$ plane is divided into regions of
$\Delta \eta \times \Delta \phi=0.1$, and each final state particle
which falls in each of these cells is set to the same $\eta$
and $\phi$ values of the center of the
corresponding cell.
%
Finally, the energy
of each final-state particle
is recalculated from the smeared $p_T^\prime$,
$\eta^\prime$ and $\phi^\prime$ values to ensure that the resulting
four-momentum is that of a light-like particle, since we neglect all
jet constituent masses in this analysis.

>>>>

Higgs pair production is simulated at leading order (LO) using
{\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}.
%
We use a tailored  model~\cite{Maltoni:2014eza}
for gluon-fusion Higgs boson pair production
which includes mass effects
from the
exact form factors for the top-quark triangle and box
loops~\cite{Plehn:1996wb}.
%
Equivalent results can be obtained using
the recently available functionalities
for the calculation of loop-induced processes
in {\tt MadGraph5\_aMC@NLO}~\cite{Hirschi:2015iia}.
%
The calculation is performed in the
$n_f$=4 scheme,  accounting for  $b$-quark mass effects. 
The renormalization and factorization
scales are taken to be $\mu_F=\mu_R=H_T/2$,
with
\be
H_T\equiv \sum_i \sqrt{p_{T,i}^2+m_i^2} \, ,
\ee
the scalar sum of the
transverse masses of all final state particles.
%
For the input parton distribution functions (PDFs) we 
adopt the NNPDF 3.0 $n_f=4$ LO set~\cite{Ball:2014uwa} with
$\alpha_s(m_Z^2)=0.118$,
interfaced via {\tt LHAPDF6}~\cite{Buckley:2014ana}.
%
The Higgs boson couplings
and branching ratios are set to their SM values,
and its mass is taken to be
$m_h=125$ GeV~\cite{Aad:2014aba,Khachatryan:2014jba,Aad:2015zhl}.
%
In the SM, the Higgs trilinear coupling
is given by $\lambda=m_h^2/2v^2$, with
$v\simeq 246$ GeV the Higgs vacuum expectation
value.
%

@@

In Fig.~\ref{fig:hhFeyn} we show representative Feynman diagrams
    for LO Higgs pair production in gluon fusion.
    %
    The non-trivial interplay between the heavy quark box and the triangle loop diagrams
    can lead to either constructive or destructive interference
    and complicates the extraction of
    the trilinear coupling
    $\lambda$ from the measurement of the Higgs pair
    production cross-section.
    %
    Higher-order corrections~\cite{deFlorian:2013jea,Frederix:2014hta}
    are dominated by gluon radiation
    from either the initial state gluons or from the heavy quark loops.

    The total inclusive cross-section for this processes is
    known up to NNLO~\cite{deFlorian:2013jea}.
    %
    Resummed NNLO+NNLL calculations for Higgs pair production are
    also available~\cite{deFlorian:2015moa},
leading to a moderate enhancement of the order of
few percent as compared to the fixed-order NNLO calculation.
%
To achieve the correct higher-order value of the
integrated cross-section, we rescale our LO signal sample to match the
NNLO+NNLL
inclusive calculation.
%
This corresponds to
a $K$-factor $\sigma_{\rm NNLO+NNLL}/\sigma_{\rm LO}=2.4$, as indicated
in Table~\ref{tab:samples}.

Parton level signal events are then showered with the {\tt Pythia8} Monte
Carlo~\cite{Sjostrand:2007gs,Sjostrand:2014zea}, version {\tt v8.201}.
%
We use the default settings for the modeling
of the underlying event (UE), multiple parton
interactions (MPI), and PU, by means
of the Monash 2013 tune~\cite{Skands:2014pea},
based on the NNPDF2.3LO PDF set~\cite{Ball:2012cx,Ball:2013hta}.
%

\subsection{Backgrounds}

Background samples are generated at leading order
with {\tt SHERPA}~\cite{Gleisberg:2008ta} {\tt v2.1.1}.
%
As in the case of the signal generation,
the NNPDF 3.0 $n_f = 4$ LO set with strong coupling
$\alpha_s(m_Z^2)=0.118$ is used for all samples, and
we use as
factorisation and renormalisation scales $\mu_F=\mu_R=H_T/2$.
%
We account for the most relevant background
processes that can mimic the
 $hh\to 4b$ signal process.
%
This includes  QCD $4b$ multi-jet production, as well as
QCD $2b2j$ and $4j$ production, and top quark pair
production.
%
The latter is restricted to the fully hadronic final state,
since 
leptonic decays of top quarks can be removed by requiring
a lepton veto.
%
Single Higgs production processes such as $Z(\to b\bar{b})h(\to b\bar{b})$
and $t\bar{t}h(\to b\bar{b})$ along with electroweak backgrounds e.g $Z(\to b\bar{b})b\bar{b}$,
are much smaller than the QCD backgrounds~\cite{Wardrope:2014kya,deLima:2014dta}
and are therefore not included in the present analysis.
%

The LO cross-sections for
the background samples have been rescaled so that the integrated
distributions reproduce known higher-order QCD results.
%
For the $4b$ and $2b2j$ samples NLO/LO $K$-factors of 1.6 and 1.3
respectively have been determined
using {\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}.
%
For the $4j$ sample, we rescale the LO cross-section
using the {\tt BLACKHAT}~\cite{Bern:2011ep}
calculation, resulting in
an NLO/LO $K$-factor of 0.6.
%
Finally, the LO cross-section for $t\bar{t}$ production has been rescaled
to match the NNLO+NNLL calculation of Ref.~\cite{Czakon:2013goa}, leading
to a $K$-factor of 1.4.
%
The $K$-factors that we use to rescale
the signal and background samples are summarised in
Table~\ref{tab:samples}.

 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
  \small
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Process &  Generator & $N_{\mathrm{evt}}$ & $\sigma_{\mathrm{LO}}$ (pb)  & $K$-factor \\
\hline
\hline
$pp \to hh$ &  {\tt MadGraph5\_aMC@NLO} & 1M & $1.7\cdot10^{-2}$  &  2.4  (NNLO+NNLL~\cite{deFlorian:2013jea,deFlorian:2015moa}) \\
\hline
\hline
$pp \to b\bar{b}b\bar{b}$ &  {\tt SHERPA}v2.1.1 & 3M &$1.1 \cdot10^3$  & 1.6 (NLO~\cite{Alwall:2014hca}) \\
$pp \to b\bar{b}jj$ &  {\tt SHERPA}v2.1.1 & 3M & $2.7 \cdot 10^5$ & 1.3 (NLO~\cite{Alwall:2014hca}) \\
$pp \to jjjj$ &  {\tt SHERPA}v2.1.1 & 3M  & $9.7\cdot 10^6$ &  0.6 (NLO~\cite{Bern:2011ep})\\
$pp \to t\bar{t}\to b\bar{b}jjjj$ &  {\tt SHERPA}v2.1.1 & 3M & $2.5\cdot 10^3$   & 1.4 (NNLO+NNLL~\cite{Czakon:2013goa})\\
\hline
\end{tabular}
\caption{\small Details of the signal and background Monte
  Carlo samples used in this work.
  %
  For top quark production, only the hadronic final state is generated.
  %
  Also provided are the inclusive $K$-factors
  which are applied to reproduce the known
  higher-order results. \label{tab:samples}
} 
\end{center}
\end{table}%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

At the generation level, the following loose selection 
cuts are applied to
background events.
%
Each final-state particle in the hard process must have $p_T \ge 20$ GeV, and be located
in the central  rapidity
region with
$| \eta | \le 3.0$.
%
At the matrix-element level
all final-state particles must also be separated by a minimum $\Delta R_{\mathrm{min}} =0.1$.
%
We have checked that these generator-level cuts are loose enough to have
no influence over the analysis cuts.
%
From Table~\ref{tab:samples}
we see that the $t\bar{t}$ and QCD $4b$ cross-sections are of
the same order of magnitude. However the former can be efficiently
reduced by using top quark reconstruction criteria.
%
The $bbjj$ cross-section is more than two orders
of magnitude larger than the $4b$ result, but will be suppressed
by the light and charm jet mis-identification rates,
required to contribute to the $4b$ final state.

@@

To account for the finite angular resolution of the calorimeter,
the $\lp \eta,\phi\rp$ plane is divided into regions of
$\Delta \eta \times \Delta \phi=0.1$, and each final state particle
which falls in each of these cells is set to the same $\eta$
and $\phi$ values of the center of the
corresponding cell.
%
Finally, the energy
of each final-state particle
is recalculated from the smeared $p_T^\prime$,
$\eta^\prime$ and $\phi^\prime$ values to ensure that the resulting
four-momentum is that of a light-like particle, since we neglect all
jet constituent masses in this analysis.
